\documentclass[letterpaper,10pt,titlepage]{article}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}

\usepackage{alltt}
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

\usepackage{geometry}
\geometry{textheight=8.5in, textwidth=6in}

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}
\usepackage{geometry}

\def\name{Sam Cooney}

%% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {cs461 ``Problem Statement''},
  pdftitle = {CS 461 Assignment 1: Problem Statement},
  pdfsubject = {CS 461 Problem Statement},
  pdfpagemode = UseNone
}

\title{CS461 Problem Statement}
\author{\name}
\date{October 2017}

\begin{document}

\begin{titlepage}
   \maketitle
\end{titlepage}

\section{Abstract}

The Investment Performance Mobile App, sponsored by Brice Lemke from HedgeServ,
is a cross-platform mobile application that will be intended for use on
iOS and Android devices. We (Sam Cooney, Avi Sinha, and Tyler Jones) as a 
team will be developing a full application that will allow fake users to
access their investment portfolios, look at current, real-time stock prices,
compare graphs and charts consisting of simulated financial date of the user
and the real time data taken from resources online. 

We will be developing a GUI that fits both Android and iOS devices that will
allow users to explore their portfolios with charts and graphs laid out in a
single easy-to-follow view. The application will also use a database holding the 
simulated data provided by HedgServ, and as well as have all the necessary 
required connections of the front to back end structures. This will include
security for users, database calls, basic algorithms for handling
real-time data, transaction history, and gains and losses.

\section{Problem Definition}

HedgServ clients are currently lacking a quick and easy way of accessing their
portfolios from their phones and tablets. They currently have to go through
the web interface to see this data but are lacking a few crucial elements that
we will be implementing in our application. These elements include: real-time 
stock prices (sometimes stocks have not been traded for a few days so stock 
prices will be misleading, our application will give recommendations on the
actual perceived value of the stocks), quick log in to one's portfolio (one click
of the app on phone's home screen), and comparison of transaction history, gains and losses, and holdings,
all in one screen. 

HedgServe has clients who use various types cell phones while working.
This requires our application to be readily available on multiple different cellular
platforms for ease of access as well. 

\section{Proposed Solution}

The Investment Performance Mobile App will be a cross-platform application
written in Xamarin and C\#. The tool will be easy to use (as defined by at least
90\% of class members who review it in senior capstone) and provide accurate real-time
stock prices taken from various resources online. It will also allow clients 
to view their holdings, gains and losses, transaction history in a simple one view
slider with graphs/charts and other various data formatting mediums. The app
will require connection to a database that houses the simulated financial data
as well as possible user log in information.



\section{Metrics}

We will have a few key performance metrics that we will be using to test our
application against. However, since our application involves a GUI we will
have to use the class for some of the testing. For this, I plan to survey 
senior capstone students to test our app, at least 90\% must anonymously 
agree that our application is easy to use and simple to navigate. 

For security,
our application must defend against multiple forms of attacks, however I am not
yet informed about the security requirements from our client so we cannot make
a decision about these metrics yet. Also, our code must pass syntax checkers for 
Xamarin and C\# without failures. An example of a syntax checkers is FxCop, which
is integrated into Visual Studio as "Code Analysis". There are others that can
and will be used as well.

For our database, we will require any and all calls
to the database have ~1 second response time (from time of request to time 
the application receives a response). We will also need our application to be
able to scale up to handle thousands of users. We do not have a requirement 
set from our client as to what the concurrent user demand and maximum user
capacity will be yet. So we will keep scalability in mind until we set these
points. Charts and graphs must be formatted correctly to fit on either iOS or
Android screens which come in varying sizes. GUI colors must match those of
HedgServ's color pallet.

\end{document}
